Liveness-Based Garbage Collection for Lazy Languages

### 2015-07-10 paper/paper.tex
Moved introduction to cell type upwards
Updated closure processing text

While exploring the heap, the  GC may encounter closures. In RGC mode,
the  closure will  be explored  as  usual. However,  \cred{  as
  mentioned earlier}, our liveness analysis predicts the liveness of
data in its evaluated form. The absence of liveness information of
closures presents challenges for LGC.

\subsection{A liveness-based garbage collection scheme}
We shall call  a unit allocatable memory as a {\em  cell}.  A cell can
hold  a  basic  value   ($\mathit{bas}$),  the  constructor  \CONS\  $(\mathit{cons~
arg_1~arg_2}$) or   a closure.  The closure, in  turn, can be  one of
($\mathit{unop~arg_1}$),  ($\mathit{ binop~arg_1~arg_2}$)  and  function  application
($\mathit{app~arg_1~arg_2})$.  Here each $\mathit{ arg_i}$ is a reference to another heap
cell or terminated through the function $\mathit{makenull}$.

>>>>

We shall call  a unit allocatable memory as a {\em  cell}.  A cell can
hold  a  basic  value   ($\mathit{bas}$),  the  constructor  \CONS\  $(\mathit{cons~
arg_1~arg_2}$) or   a closure.  The closure, in  turn, can be  one of
($\mathit{unop~arg_1}$),  ($\mathit{ binop~arg_1~arg_2}$)  and  function  application
($\mathit{app~arg_1~arg_2})$.  Here each $\mathit{ arg_i}$ is a reference to another heap
cell or terminated through the function $\mathit{makenull}$.

While exploring the heap, the GC  may encounter closures. In RGC mode,
the  closure will  be  explored as  usual and  copied  by passing  the
references. Since our liveness analysis  predicts the liveness of data
in its evaluated form only, closures  present a challenge for LGC. LGC
will need  to map the  liveness of the  free variables of  the closure
back  to their  evaluation point.  This  situation can  be handled  in
multiple ways and hence we present 2 algorithms for handling closures.

\subsection{A liveness-based garbage collection scheme}
